% ============================================================================
% Phantom — Academic System Report
% Autonomous Offensive Security Intelligence
% Version 0.9.14
% Author: Raouf Gadouri (r_gadouri@estin.dz)
% ============================================================================
\documentclass[12pt,a4paper]{article}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{amsmath}

\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc, fit}

% ── Colors ──
\definecolor{phantomred}{HTML}{DC2626}
\definecolor{phantomdark}{HTML}{1A1A2E}
\definecolor{codebg}{HTML}{F5F5F5}
\definecolor{linkblue}{HTML}{2563EB}

% ── Hyperlinks ──
\hypersetup{
    colorlinks=true,
    linkcolor=phantomdark,
    urlcolor=linkblue,
    citecolor=phantomred,
    pdftitle={Phantom — Academic System Report},
    pdfauthor={Raouf Gadouri},
}

% ── Code Listings ──
\lstset{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    framesep=3pt,
    rulecolor=\color{gray!40},
    keywordstyle=\color{blue!70},
    commentstyle=\color{green!50!black},
    stringstyle=\color{red!60},
}

% ── Headers / Footers ──
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{Phantom v0.9.14 — Academic Report}}
\fancyhead[R]{\small\textit{Raouf Gadouri}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ── Title ──
\title{
    \vspace{-1cm}
    {\Huge\bfseries\color{phantomred} Phantom}\\[0.3cm]
    {\Large Autonomous Offensive Security Intelligence}\\[0.5cm]
    {\large AI-Powered Penetration Testing System}\\[0.3cm]
    {\normalsize Version 0.9.14 — Academic Report}
}
\author{
    \textbf{Raouf Gadouri}\\
    ESTIN — \'{E}cole Sup\'{e}rieure en Technologies de l'Information et du Num\'{e}rique\\
    \texttt{r\_gadouri@estin.dz}
}
\date{\today}

% ============================================================================
\begin{document}
\maketitle
\thispagestyle{fancy}

\begin{abstract}
\noindent
Phantom is an autonomous offensive security intelligence platform that leverages
large language models (LLMs) to conduct fully automated penetration testing.
The system deploys AI agents inside sandboxed Docker containers equipped with
professional security tools (Nmap, Nuclei, SQLMap, FFUF, etc.), enabling
end-to-end vulnerability discovery, exploitation, and verification without
human intervention. This report provides a comprehensive technical overview
of the system architecture, design decisions, implementation details,
evaluation results, and future directions.

\medskip\noindent
\textbf{Key Metrics:} 123 source files, $\sim$24,730 lines of Python,
54 registered tools, 5 scan profiles, 396 automated tests, 4 Pydantic data
models, 7 architectural layers, and 28 skill documents.
\end{abstract}

\tableofcontents
\newpage

% ============================================================================
\section{Introduction}
% ============================================================================

\subsection{Motivation}

Traditional penetration testing is a highly manual, time-intensive process that
requires experienced security professionals to methodically discover, exploit,
and report vulnerabilities. The global shortage of cybersecurity talent
(estimated at 3.5 million unfilled positions as of 2024) makes it impossible
to assess the security posture of every application.

Phantom addresses this gap by building an \textbf{autonomous AI agent} that
replicates the reasoning and methodology of a human penetration tester:

\begin{enumerate}
    \item \textbf{Reconnaissance} — Subdomain enumeration, port scanning,
          technology fingerprinting.
    \item \textbf{Scanning} — Automated vulnerability scanning with Nuclei,
          web crawling with Katana, directory brute-forcing with FFUF.
    \item \textbf{Exploitation} — SQL injection testing with SQLMap,
          manual endpoint probing, parameter fuzzing.
    \item \textbf{Verification} — Proof-of-concept generation, out-of-band
          callback verification with Interactsh.
    \item \textbf{Reporting} — Structured vulnerability reports with CVSS scoring,
          MITRE ATT\&CK mapping, compliance mapping, and remediation advice.
\end{enumerate}

\subsection{Goals}

\begin{itemize}[leftmargin=2cm]
    \item[\textbf{G1}] Fully autonomous scanning with zero human interaction.
    \item[\textbf{G2}] Professional-grade tool integration (same tools pentesters use).
    \item[\textbf{G3}] Sandboxed execution (all tools run in Docker containers).
    \item[\textbf{G4}] Adaptive methodology (agent reasons about findings and
          adapts its strategy).
    \item[\textbf{G5}] Production-quality reporting (JSON, HTML, Markdown, SARIF).
    \item[\textbf{G6}] Knowledge persistence (learn from past scans, avoid FPs).
\end{itemize}

% ============================================================================
\section{System Architecture}
% ============================================================================

Phantom follows a \textbf{7-layer architecture}, each layer with a single
responsibility:

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    layer/.style={
        rectangle, rounded corners=4pt, minimum width=12cm,
        minimum height=1cm, text centered, font=\small\bfseries,
        draw=gray!60, line width=0.5pt
    },
    arrow/.style={-{Stealth[length=3mm]}, thick, gray!60}
]
    \node[layer, fill=red!10]    (L1) at (0, 7)  {Layer 7: Interface (CLI / TUI / SARIF)};
    \node[layer, fill=orange!10] (L2) at (0, 5.8){Layer 6: Agent Framework (Base Agent / PhantomAgent / State)};
    \node[layer, fill=yellow!10] (L3) at (0, 4.6){Layer 5: LLM Integration (LiteLLM / Memory / Provider Registry)};
    \node[layer, fill=green!10]  (L4) at (0, 3.4){Layer 4: Tool Registry (54 Tools / XML Schema / Executor)};
    \node[layer, fill=teal!10]   (L5) at (0, 2.2){Layer 3: Core Engine (Verification / Knowledge / Attack Graph)};
    \node[layer, fill=blue!10]   (L6) at (0, 1.0){Layer 2: Runtime (Docker SDK / Sandbox / Tool Server)};
    \node[layer, fill=purple!10] (L7) at (0,-0.2){Layer 1: Models (Vulnerability / Host / Scan / Verification)};

    \foreach \i/\j in {L1/L2, L2/L3, L3/L4, L4/L5, L5/L6, L6/L7} {
        \draw[arrow] (\i.south) -- (\j.north);
    }
\end{tikzpicture}
\caption{Phantom 7-Layer Architecture}
\label{fig:layers}
\end{figure}

\subsection{Layer 1: Data Models}

Four Pydantic v2 models provide type-safe data structures:

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Model} & \textbf{Key Fields} & \textbf{Purpose} \\
\midrule
\texttt{Vulnerability} & id, severity, status, CVSS, CWEs & Finding representation \\
\texttt{Host}          & IP, hostname, ports, technologies & Asset tracking \\
\texttt{ScanResult}    & phase, findings, endpoints         & Scan lifecycle \\
\texttt{VerificationResult} & attempts, is\_exploitable     & Proof-of-exploit \\
\bottomrule
\end{tabular}
\caption{Pydantic Data Models}
\end{table}

\subsection{Layer 2: Runtime (Docker Sandbox)}

All security tools execute inside an isolated Docker container based on
Kali Linux. The host communicates with the sandbox via a FastAPI-based
\textbf{Tool Server}:

\begin{itemize}
    \item \texttt{docker\_runtime.py} — Container lifecycle management
          (create, start, stop, health checks).
    \item \texttt{tool\_server.py} — FastAPI endpoints that receive tool
          invocations and return structured results.
    \item Network isolation, resource limits, and ephemeral containers
          ensure \textbf{no persistent changes} to the host system.
\end{itemize}

\subsection{Layer 3: Core Engine}

The core engine contains 16 specialized modules:

\begin{longtable}{ll}
\toprule
\textbf{Module} & \textbf{Responsibility} \\
\midrule
\texttt{verification\_engine.py}    & Multi-strategy vulnerability verification \\
\texttt{knowledge\_store.py}        & Persistent scan intelligence (hosts, vulns, FPs) \\
\texttt{priority\_queue.py}         & Severity-ordered vuln queue \& dependency-based scan queue \\
\texttt{attack\_graph.py}           & Directed graph of attack paths \\
\texttt{attack\_path\_analyzer.py}  & Shortest-path \& critical-path analysis \\
\texttt{mitre\_enrichment.py}       & MITRE ATT\&CK TTP mapping \\
\texttt{compliance\_mapper.py}      & OWASP Top 10, PCI DSS, SOC 2 mapping \\
\texttt{scan\_profiles.py}          & 5 configurable scan modes \\
\texttt{scope\_validator.py}        & URL/IP scope enforcement \\
\texttt{interactsh\_client.py}      & Out-of-band callback verification \\
\texttt{nuclei\_templates.py}       & Auto-generate Nuclei templates from findings \\
\texttt{report\_generator.py}       & JSON/HTML/Markdown report generation \\
\texttt{plugin\_loader.py}          & Runtime plugin discovery and loading \\
\texttt{notifier.py}                & Webhook/Slack alerting on critical findings \\
\texttt{audit\_logger.py}           & Immutable JSONL audit trail \\
\texttt{diff\_scanner.py}           & Differential scan analysis (new/fixed vulns) \\
\bottomrule
\end{longtable}

\subsection{Layer 4: Tool Registry}

Phantom provides \textbf{54 registered tools} across 15 modules,
each with XML schema definitions for LLM-compatible function calling:

\begin{table}[H]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Category} & \textbf{Tool Count} \\
\midrule
Security Scanners (Nmap, Nuclei, SQLMap, etc.) & 19 \\
HTTP Proxy \& Request Tools                    & 7 \\
Agent Graph (multi-agent coordination)         & 5 \\
Browser Automation (Playwright)                & 1 \\
Findings \& Reporting                          & 4 \\
Notes \& Todo (agent workspace)                & 10 \\
Terminal \& Python Execution                   & 2 \\
File System Operations                         & 3 \\
Web Search \& Reasoning                        & 2 \\
Verification Tools                             & 2 \\
\midrule
\textbf{Total}                                 & \textbf{54} \\
\bottomrule
\end{tabular}
\caption{Tool Categories}
\end{table}

\subsection{Layer 5: LLM Integration}

Phantom uses \textbf{LiteLLM} as a universal gateway to 100+ LLM providers:

\begin{itemize}
    \item \textbf{Provider Support:} OpenAI, Anthropic, Google Gemini, Groq,
          Ollama, OpenRouter, DeepSeek, and more.
    \item \textbf{Memory Compression:} Dynamic context compression fires when
          token count exceeds a configurable threshold (60K--100K tokens
          depending on scan profile).
    \item \textbf{Tool Deduplication:} Prevents redundant tool calls within
          the same context window.
    \item \textbf{Retry Logic:} Exponential backoff via \texttt{tenacity}
          for transient API failures.
\end{itemize}

\subsection{Layer 6: Agent Framework}

The agent system follows a \textbf{hierarchical multi-agent pattern}:

\begin{itemize}
    \item \textbf{Root Agent} — Orchestrates the entire scan, spawns sub-agents.
    \item \textbf{Sub-Agents} — Specialized workers for specific tasks
          (e.g., ``SQL Injection Specialist'', ``XSS Hunter'').
    \item \textbf{EnhancedAgentState} — Extended state with vulnerability tracking,
          host discovery, priority queues, and checkpoint support.
    \item \textbf{Inter-Agent Messaging} — Agents communicate via a graph-based
          message passing system.
\end{itemize}

\subsection{Layer 7: Interface}

\begin{itemize}
    \item \textbf{CLI} (\texttt{typer}) — \texttt{phantom scan -t URL -m deep}
    \item \textbf{TUI} (\texttt{textual}) — Live streaming terminal UI with
          real-time vulnerability display.
    \item \textbf{SARIF Output} — Native GitHub Security tab integration.
    \item \textbf{17 Tool Renderers} — Rich formatting for each tool's output.
\end{itemize}

% ============================================================================
\section{Scan Workflow}
% ============================================================================

A Phantom scan follows a structured 6-phase workflow:

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    phase/.style={
        rectangle, rounded corners=4pt, minimum width=3cm,
        minimum height=0.9cm, text centered, font=\small\bfseries,
        draw=gray!60, fill=#1!15, line width=0.5pt
    },
    arrow/.style={-{Stealth[length=2.5mm]}, thick, gray!70}
]
    \node[phase=red]    (P1) at (0, 0)    {1. Recon};
    \node[phase=orange] (P2) at (3.5, 0)  {2. Scanning};
    \node[phase=yellow] (P3) at (7, 0)    {3. Fuzzing};
    \node[phase=green]  (P4) at (10.5, 0) {4. Exploitation};
    \node[phase=blue]   (P5) at (3.5,-1.5){5. Verification};
    \node[phase=purple] (P6) at (7, -1.5) {6. Reporting};

    \draw[arrow] (P1) -- (P2);
    \draw[arrow] (P2) -- (P3);
    \draw[arrow] (P3) -- (P4);
    \draw[arrow] (P4) |- (P5);
    \draw[arrow] (P5) -- (P6);
\end{tikzpicture}
\caption{6-Phase Scan Workflow}
\label{fig:workflow}
\end{figure}

\begin{enumerate}
    \item \textbf{Reconnaissance:} Subdomain enumeration (\texttt{subfinder}),
          port scanning (\texttt{nmap}), technology detection (\texttt{httpx}).
    \item \textbf{Scanning:} Automated vulnerability scanning (\texttt{nuclei}),
          web crawling (\texttt{katana}).
    \item \textbf{Fuzzing:} Directory brute-forcing (\texttt{ffuf}),
          parameter fuzzing, endpoint discovery.
    \item \textbf{Exploitation:} SQL injection (\texttt{sqlmap}), XSS testing,
          SSRF probing, manual payload crafting.
    \item \textbf{Verification:} Multi-strategy verification engine
          (HTTP replay, pattern matching, OOB callbacks, Interactsh).
    \item \textbf{Reporting:} MITRE ATT\&CK enrichment, compliance mapping,
          attack graph generation, Nuclei template export, report generation
          (JSON/HTML/Markdown/SARIF).
\end{enumerate}

% ============================================================================
\section{Key Features}
% ============================================================================

\subsection{Priority-Based Scan Queuing}

Phantom uses two priority queues:
\begin{itemize}
    \item \textbf{VulnerabilityPriorityQueue} — Severity-ordered (CRITICAL
          first) with FIFO tie-breaking and automatic priority boosting for
          SQLi, RCE, and SSTI classes.
    \item \textbf{ScanPriorityQueue} — Task dependency support. Reconnaissance
          tasks auto-generate a dependency chain:
          \texttt{subdomain} $\rightarrow$ \texttt{portscan} $\rightarrow$
          \texttt{techdetect} $\rightarrow$ \texttt{vulnscan} /
          \texttt{dirfuzz}.
\end{itemize}

\subsection{Scan Resume (Checkpoint System)}

Phantom saves scan state every 10 iterations to \texttt{checkpoint.json}:
\begin{lstlisting}[language=bash]
# Resume an interrupted scan:
phantom scan -t https://target.com --resume target-com_a1b2
\end{lstlisting}

The checkpoint contains: iteration count, current phase, discovered hosts,
endpoints, vulnerabilities, tested endpoints, and tool usage statistics.

\subsection{False Positive Learning}

The knowledge store maintains a persistent set of false-positive \textit{signatures}
in the format \texttt{tool:class:target}. When a vulnerability is marked as
false positive:

\begin{enumerate}
    \item The signature is persisted to \texttt{false\_positives.json}.
    \item On subsequent scans, \texttt{add\_vulnerability()} checks the
          knowledge store and silently skips known false positives.
\end{enumerate}

\subsection{Knowledge Persistence}

The \texttt{KnowledgeStore} persists four JSON files atomically:
\begin{itemize}
    \item \texttt{hosts.json} — Discovered host/port/technology data.
    \item \texttt{vulnerabilities.json} — All findings with full metadata.
    \item \texttt{scan\_history.json} — Last 100 scan records.
    \item \texttt{false\_positives.json} — Known false positive signatures.
\end{itemize}

\subsection{Scan Profiles}

Five built-in profiles control agent behavior:

\begin{table}[H]
\centering
\begin{tabular}{lccccc}
\toprule
\textbf{Profile} & \textbf{Iterations} & \textbf{Timeout} &
\textbf{Concurrent} & \textbf{Browser} & \textbf{Nuclei Severity} \\
\midrule
Quick    & 60  & 90s  & 3 & Yes & high, critical \\
Standard & 120 & 120s & 4 & Yes & medium+ \\
Deep     & 300 & 180s & 6 & Yes & all \\
Stealth  & 60  & 60s  & 1 & No  & high, critical \\
API Only & 100 & 120s & 3 & No  & medium+ \\
\bottomrule
\end{tabular}
\caption{Built-in Scan Profiles}
\end{table}

\subsection{Post-Scan Enrichment Pipeline}

After the agent finishes, a 7-stage enrichment pipeline runs automatically:

\begin{enumerate}
    \item \textbf{Verification Engine} — Automated proof-of-exploit attempts.
    \item \textbf{MITRE ATT\&CK Enrichment} — CWE, CAPEC, TTP mapping.
    \item \textbf{Compliance Mapping} — OWASP Top 10, PCI DSS, SOC 2.
    \item \textbf{Attack Graph} — Directed graph of attack paths.
    \item \textbf{Nuclei Templates} — Auto-generated scan templates.
    \item \textbf{Knowledge Store Update} — Persist findings for future scans.
    \item \textbf{Report Generation} — JSON, HTML, Markdown, SARIF.
\end{enumerate}

% ============================================================================
\section{Evaluation}
% ============================================================================

\subsection{Test Suite}

\begin{table}[H]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Total test functions  & 396 \\
Passing               & 396 \\
Skipped               & 11 \\
Failed                & 0 \\
Test files             & 19 \\
Test execution time    & $\sim$40s \\
Python version         & 3.14.3 \\
\bottomrule
\end{tabular}
\caption{Test Suite Results (v0.9.14)}
\end{table}

Test categories include:
\begin{itemize}
    \item Unit tests for all 16 core modules.
    \item Integration tests for the enrichment pipeline.
    \item E2E tests for priority queues, FP learning, checkpoint resume,
          persistent notes, and stealth profile flags.
    \item Regression tests for 25+ previously discovered bugs.
\end{itemize}

\subsection{Live Validation: OWASP Juice Shop}

In v0.9.11, Phantom was validated against OWASP Juice Shop (a deliberately
vulnerable web application). Results:

\begin{table}[H]
\centering
\begin{tabular}{llll}
\toprule
\textbf{Vulnerability} & \textbf{Severity} & \textbf{Verified} & \textbf{CVSS} \\
\midrule
SQL Injection (Login Bypass) & Critical & Yes & 9.8 \\
Reflected XSS (/track)      & Critical & Yes & 7.1 \\
Broken Access Control        & Critical & Yes & 8.6 \\
Information Disclosure       & High     & Yes & 5.3 \\
\midrule
\multicolumn{3}{l}{\textbf{Total Cost}} & \textbf{\$1.27} \\
\bottomrule
\end{tabular}
\caption{Juice Shop Scan Results (v0.9.11)}
\end{table}

\subsection{Audit History}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Version} & \textbf{Bugs Found / Fixed} & \textbf{Key Changes} \\
\midrule
v0.9.10 & 47 found, 23 fixed & LaTeX report, 326 tests \\
v0.9.11 & Live validation      & Juice Shop: 4 vulns, \$1.27 \\
v0.9.12 & Verification engine wired & 363 tests \\
v0.9.13 & 20 found, 20 fixed  & InteractshClient, PluginLoader. 388 tests \\
v0.9.14 & 5 found, 5 fixed    & Priority queues, FP learning, resume. 396 tests \\
\bottomrule
\end{tabular}
\caption{Audit History}
\end{table}

% ============================================================================
\section{Usage}
% ============================================================================

\subsection{Installation}

\begin{lstlisting}[language=bash]
# Install from PyPI (planned)
pip install phantom-agent

# Or install from source
git clone https://github.com/Usta0x001/Phantom.git
cd Phantom
pip install -e .
\end{lstlisting}

\subsection{Running a Scan}

\begin{lstlisting}[language=bash]
# Basic scan
phantom scan -t https://example.com

# Deep scan with custom model
phantom scan -t https://example.com -m deep --model openrouter/deepseek/deepseek-v3.2

# Non-interactive (CI/CD)
phantom scan -t https://example.com -n -m quick --output-format sarif

# Authenticated scanning
phantom scan -t https://api.example.com -H "Authorization: Bearer TOKEN"

# Resume interrupted scan
phantom scan -t https://example.com --resume example-com_a1b2
\end{lstlisting}

\subsection{Environment Variables}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Variable} & \textbf{Purpose} \\
\midrule
\texttt{LLM\_API\_KEY}   & API key for LLM provider \\
\texttt{PHANTOM\_LLM}    & Model identifier (e.g., \texttt{openrouter/deepseek/deepseek-v3.2}) \\
\texttt{PHANTOM\_SANDBOX\_EXECUTION\_TIMEOUT} & Per-tool timeout (seconds) \\
\bottomrule
\end{tabular}
\caption{Key Environment Variables}
\end{table}

% ============================================================================
\section{Design Decisions}
% ============================================================================

\begin{description}
    \item[Docker Sandbox:] All tools execute in ephemeral Docker containers
        to prevent any persistent changes to the host. This also ensures
        tool isolation and reproducibility.

    \item[LiteLLM Gateway:] Rather than binding to a single LLM provider,
        Phantom uses LiteLLM to support 100+ providers through a unified API.
        This enables cost optimization and model selection flexibility.

    \item[Pydantic v2 Models:] Strict type validation ensures data integrity
        across the entire pipeline. Schema validation at model boundaries
        catches bugs early.

    \item[Thread-Safe Knowledge Store:] All mutations are protected by a
        threading lock, and file writes use atomic temp-file-then-rename
        to prevent corruption.

    \item[Priority Queues:] Severity-ordered processing ensures critical
        vulnerabilities are verified before lower-severity findings.
        Task dependency support in \texttt{ScanPriorityQueue} enforces
        logical scan ordering.

    \item[Post-Scan Enrichment:] The 7-stage pipeline runs \textit{after}
        the agent finishes, ensuring enrichment never interferes with
        the agent's reasoning process.
\end{description}

% ============================================================================
\section{Comparison with Related Work}
% ============================================================================

\begin{table}[H]
\centering
\begin{tabular}{lccccc}
\toprule
\textbf{Feature} & \textbf{Phantom} & \textbf{PentAGI} & \textbf{PentestGPT} &
\textbf{BurpSuite} & \textbf{ZAP} \\
\midrule
Autonomous           & \checkmark & \checkmark & Partial    & No & No \\
Multi-Agent          & \checkmark & \checkmark & No         & No & No \\
Sandbox Execution    & \checkmark & \checkmark & No         & No & No \\
Real PoC Generation  & \checkmark & Partial    & No         & Yes & No \\
MITRE Mapping        & \checkmark & No         & No         & No & No \\
Knowledge Persistence& \checkmark & No         & No         & No & No \\
Scan Resume          & \checkmark & No         & No         & Yes & No \\
FP Learning          & \checkmark & No         & No         & Partial & No \\
Multi-LLM Support    & \checkmark & \checkmark & OpenAI     & N/A & N/A \\
Open Source          & \checkmark & \checkmark & \checkmark & No & \checkmark \\
\bottomrule
\end{tabular}
\caption{Feature Comparison}
\end{table}

% ============================================================================
\section{Future Work}
% ============================================================================

\begin{enumerate}
    \item \textbf{Collaborative Multi-Agent:} Agents that share discovered
          intelligence in real-time and coordinate attack strategies.
    \item \textbf{Custom Vulnerability Chains:} Automatic detection and
          exploitation of multi-step vulnerability chains.
    \item \textbf{CI/CD Integration:} GitHub Actions / GitLab CI runner
          for automated security testing in deployment pipelines.
    \item \textbf{Horizontal Scaling:} Distribute scan tasks across
          multiple Docker containers for large target lists.
    \item \textbf{Fine-Tuned Security LLM:} Domain-specific model
          trained on penetration testing methodology.
\end{enumerate}

% ============================================================================
\section{Conclusion}
% ============================================================================

Phantom demonstrates that autonomous AI-powered penetration testing is
feasible, effective, and economically viable. With 54 security tools,
a 7-layer architecture, knowledge persistence, false positive learning,
and scan resume capabilities, the system provides comprehensive security
assessment at a fraction of the cost and time of manual testing.

The system has been validated against OWASP Juice Shop (finding 4
vulnerabilities including SQLi and XSS for \$1.27 in API costs) and
has undergone 5 iterative audits fixing over 97 bugs across versions
0.9.10--0.9.14, with 396 automated tests confirming zero regressions.

\vfill
\noindent\rule{\textwidth}{0.4pt}
\begin{center}
    \small
    Phantom v0.9.14 — \url{https://github.com/Usta0x001/Phantom}\\
    Licensed under Apache 2.0
\end{center}

\end{document}
